---
title: "3-23"
format: html
editor: visual
---

```{r}
library(tidyverse)
prisons <- read.csv("Prison_Boundaries.csv")
```

# Question 1: What have been some issues you’ve had with this setup? Can data be condensed?

- Missing variables/values
- Several data frames
- Not having unique identifiers (example: V1, V2)
- Different types


# Question 2: What happens when we create a vector with two types represented in it? Is there a hierarchy to these types?

```{r}
x4 <- c(2, "times", TRUE, 4)
print(x4)
typeof(x4)
```

It prints them all out as character types because it's the lowest in the hierarchy (integer, logical, double, character) and it's the most flexible type.

# Question 3: Use the + and mean() operations on the following vectors:

```{r}
x1 <- c(1, 2, 3, 4, 5)
x2 <- c("a", "b", "c", "d", "e")
x3 <- c(TRUE, FALSE, FALSE, TRUE, FALSE)

x1 + x3
# x2 + x3 <- error

mean(x1)
mean(x2) # gets a warning message because "argument is not numeric or logical; returns NA
mean(x3)
```

# Question 4: Using sapply(prisons, typeof), identify which columns in the data frame have an improper data type.

```{r}
sapply(prisons, typeof)
```
It seems like SOURCEDATE, VAL_DATE, CreationDate, and EditDate have improper data types, because they're being treated as characters and not dates.

# Question 5: For two of these variables mentioned in Q4, correct the data type using prior code.

```{r}
library(lubridate)

prisons <-
  prisons |>
  mutate(SOURCEDATE = as.Date(SOURCEDATE),
         VAL_DATE = as.Date(VAL_DATE))

sapply(prisons, class)
```


# Question 6: Using the cheatsheet mentioned earlier, try out two different lubridate functions on the date/time column in the prisons dataset.

```{r}
prisons |>
  mutate(SOURCEDATE = week(SOURCEDATE),
         VAL_DATE = tz(VAL_DATE))
```

