---
title: "Reading Exercise #1"
format: html
editor: visual
---

Problem #1:

```{r}
mtcars |>
  select(mpg, cyl)
```

This code chunk is wrong because select() comes from dplyr, which you need to use library(dplyr) and then you can use select().

Problem #3:

```{r}
obj1 <- 2:10
obj2 <- c(2, 5)
obj3 <- c(TRUE, FALSE)
obj4 <- 42

obj1 * 10
obj1[2:4]
obj1[-3]
obj1 + obj2
obj1 * obj3
obj1 + obj4
obj2 + obj3
sum(obj2)
sum(obj3)
```

obj1 <- 2:10 means range from 2-10
obj2 <- c(2,5) means just returning the values 2 and 5
obj3 <- c(TRUE, FALSE) means just returning TRUE and FALSE
obj4 <- 42 is literally just 42

obj1*10 would result in 20, 30, 40, 50, 60, 70, 80, 90, and 100
obj1[2:4] would result in 3, 4, 5
obj1[-3] would result in 2, 3, 5, 6, 7, 8, 9, 10
obj1 + obj2 would result in 4, 8, 6, 10, 8, 12, 10, 14, 12
obj1 * obj3 would result in 2, 0, 4, 0, 6, 0, 8, 0, 10
obj1 + obj4 would result in 44, 45, 46, 47, 48, 49, 50, 51, 52
obj2 + obj3 would result in 3, 5
sum(obj2) would result in 7
sum(obj3) would result in 1

